Scholten Read Sanborn

### 2015-11-16 shinyapps/scholtenReadSanborn2014.Rmd
add interval model

int_fn <- function(sstime, lltime, alpha, theta, beta, tau) {

  sstime <- as.numeric(sstime)
  lltime <- as.numeric(lltime)
  alpha <- as.numeric(alpha)
  theta <- as.numeric(theta)
  beta <- as.numeric(beta)

  (1 + alpha * ((w_t(lltime) - w_t(sstime))/theta)^theta) ^(-beta/alpha)
}

int_df <- data.frame(int_len = 0:100)

int_df1 <- int_df %>%
  mutate(sstime =,
         lltime,
         alpha,
         theta,
         beta)

@@

```{r, echo=FALSE}
inputPanel(
  textInput("inton", "Interval onset"),
  textInput("intlen", "Larger Later time"),
  textInput("beta", "beta > 0 delay"),
  textInput("tau", "tau > departure from exponential discounting")
  )

>>>>

int_fn <- function(int_len, int_onset, alpha, theta, beta, tau) {

  int_len <- as.numeric(int_len)
  int_onset <- as.numeric(int_onset)
  alpha <- as.numeric(alpha)
  theta <- as.numeric(theta)
  beta <- as.numeric(beta)

  sstime <- int_onset
  lltime <- sstime + int_len

  (1 + alpha * ((w_t(lltime, tau) - w_t(sstime, tau))/theta)^theta) ^(-beta/alpha)
}

int_df <- data.frame(int_len = 1:100)

int_df1 <- int_df %>%
  mutate(int_onset = 1, 
         alpha = .1, theta = .1, beta = .1, tau = .1)

mutate(int_df1, delta = int_fn(int_len, int_onset, alpha, theta, beta, tau))

@@

```{r, echo=FALSE}
inputPanel(
  sliderInput("inton", "Interval onset", min=0, max = 365, step=1, value= 10),
  sliderInput("alpha", "alpha > 0 subadditivity", min=.01, max = 2, step=.05, value= 0),
  sliderInput("beta", "beta > 0 delay", min=0, max = 1, step=.05, value= .5),
  sliderInput("theta", "theta > 1 superadditive", min=1, max = 3, step=.05, value= 1),
  sliderInput("tau", "tau > 0 diminishing absolute sensitivity", min=.001, max = 1, step=.05, value= .01)
  )

renderPlot({
  int_df$inton <- input$inton
  int_df$alpha <- input$alpha
  int_df$beta <- input$beta
  int_df$theta <- input$theta
  int_df$tau <- input$tau

  int_df <- transform(int_df, delta = int_fn(int_len, inton, alpha, theta, beta, tau))

    int_df <- transform(int_df, daily = delta ^ (1/int_len))

  ggplot(int_df, aes(x = int_len, y = daily, group = 1)) +
    geom_line() +
#     geom_abline(intercept = 0, slope=0) +
#     geom_vline(xintercept = 0) +
#     xlab("Outcome") +
#     ylab("Value") +
    ylim(c(0, 1))
})
